Deciding Bitvector Termination with Program Synthesis

### 2014-07-02 papers/termination/paper.tex
Nontermination

Given that our state space is finite, a transition relation induces a infinite execution if and only if some state is 
visited twice in the course of the execution. Hence, an alternative formulation of the non-termination problem 
for bit-vectors may search for a state that is visited twice.
However, this would require reasoning about the transitive closure of the transition relation.\\

>>>>

Given that our program's state space is finite, a transition relation induces a infinite execution if and only if some state is 
visited infinitely often, or equivalently if the state is visitied twice in the course of the execution.
This gives us an alternative way of expression a non-termination proof: we can can try to find a witness $x$ to the satisfiability
of the formula
$$ \exists x . T^+(x, x)$$
However, deciding satisfiability of this formula directly requires a logic that includes a transitive closure operator, which
ours does not have.\\
